\Title

### 2021-02-03 latex/paper/main.tex
Started the paper. For some reason citations are not numbers.

\documentclass[journal,twoside,web]{ieeecolor}
\usepackage{generic}
%/========== Preamble ==========/%
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
%---------- Bibliography Style ----------%
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
%---------- Header ----------% 
\newcommand*{\Title}{VNHC and Acrobot Title}
\markboth{\journalname, VOL. XX, NO. XX, XXXX 2021}
{Moran-MacDonald \MakeLowercase{\textit{et al.}}: \Title}
%/========== /Preamble ==========/%

@@

\subsection{Notation}

@@

%/========== VNHC ==========/%
\section{Theory of VNHCs}\label{sec:vnhc}
Just like in the thesis, cover the theory of VNHCs. Justify our results compared
to those of Horn. Make it terse but legible. Cover simply actuated systems,
vnhcs, regularity, the theorems, etc.

@@

\end{document}
%/========== /Main Document ==========/%
% vim: set tw=80 ts=4 sw=4 sts=0 et ffs=unix :

>>>>

\documentclass[journal,twoside,web]{ieeecolor}
\usepackage{generic}
%/========== Preamble ==========/%
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}

%---------- Bibliography Style ----------%
\bibliographystyle{IEEEtranN}

%---------- Header ----------% 
\newcommand*{\Title}{VNHC and Acrobot Title}
\markboth{\journalname, VOL. XX, NO. XX, XXXX 2021}
{Moran-MacDonald \MakeLowercase{\textit{et al.}}: \Title}

%---------- Special Commands ----------%
\newcommand*{\tpose}{^\mathsf{T}} 
\newcommand*{\inv}{^\mathsf{-1}}
\newcommand*{\Rt}[1]{[\R]_{#1}}
\newcommand*{\R}{\mathbb{R}}
\newcommand*{\n}{\mathbf{n}}
\newcommand*{\N}{\mathbb{N}}
\newcommand*{\Sone}{\mathbb{S}^1}
\newcommand*{\SxR}{\Sone \times \R}
\newcommand*{\Minv}{M^\mathsf{-1}}
\newcommand*{\Id}[1]{I_{#1}}
\newcommand*{\Zmat}[1]{\bm{0}_{#1}}
\newcommand*{\diff}[2]{\frac{d #1}{d #2}}
\newcommand*{\ddiff}[3]{\frac{d^2 #1}{d #2 d #3}}
\newcommand*{\pdiff}[2]{\frac{\partial #1}{\partial #2}}
%/========== /Preamble ==========/%

@@

\subsection{Notation}
We use the following notation in this paper. 
For \(T > 0\), the set of real numbers modulo is denote \(\Rt{T}\), with
\(\Rt{\infty} := \R\).
The gradient of the matrix-valued function 
\(A : \R^m \rightarrow \R^{n\times n}\) is the matrix of stacked partial
derivatives, 
\(\nabla_xA := (\pdiff{A}{x_1},\ldots,\pdiff{A}{x_m})\tpose \in \R^{nm \times n}\).
Given two matrices \(A \in \R^{n \times m}\) and \(B \in \R^{r \times s}\), the
Kronecker product \cite{kronprod} \(A \otimes B \in \R^{nr \times ms}\) is the
matrix
\[
    A \otimes B = \begin{bmatrix}
        A_{1,1}B & \cdots & A_{1,m} B \\
        \vdots & \ddots & \vdots \\
        A_{n,1} B & \cdots & A_{n,m} B
    \end{bmatrix} 
    .
\]

@@

%/========== VNHC ==========/%
\section{Theory of VNHCs}\label{sec:vnhc}
TODO: Just like in the thesis, cover the theory of VNHCs. Justify our results compared
to those of Horn. Make it terse but legible. Cover simply actuated systems,
vnhcs, regularity, the theorems, etc.

\subsection{Simply Actuated Hamiltonian Systems}
Take an underactuated mechanical system modelled with generalized coordinates 
\(q = (q_1, \ldots, q_n)\) on the configuration manifold
\(\mathcal{Q} = \Rt{T_1} \times \cdot \Rt{T_n}\), where
\(T_i = 2\pi\) if \(q_i\) is an angle and \(T_i = \infty\) if \(q_i\) is a
length. The corresponding velocities are 
\(\dot{q} = (\dot{q}_1,\ldots,\dot{q}_n) \in \R^n\).

Suppose this system has Lagrangian
\(\mathcal{L}(q,\dot{q}) = 1/2 \dot{q}^T D(q) \dot{q} - P(q)\),
where \(P : \mathcal{Q} \rightarrow \mathbb{R}\) is the potential energy, and
the inertia matrix \(D : \mathcal{Q} \rightarrow \mathbb{R}^{n \times n}\)
is positive definite for all \(q \in \mathcal{Q}\).
By defining the \textit{conjugate of momentum} 
\(p_i := \pdiff{\mathcal{L}}{\dot{q}_i}\) so that the vector 
\(p = (p_1,\ldots,p_n) \in \R^n\) is given by \(p = D(q)\dot{q}\),
we find the \textit{Hamiltonian} of the system in \((q,p)\) coordinates is
\(\mathcal{H}(q,p) = 1/2 p\tpose D(q) p + P(q)\) \cite{landau_mechanics}.
The dynamics of the system in Hamiltonian form are
\begin{equation}\label{eqn:hamiltonian-eom-general}
    \begin{cases}
        \dot{q} = \nabla_p\mathcal{H} 
        , \\
        \dot{p} = -\nabla_q\mathcal{H} + \tau
        ,
    \end{cases}
\end{equation}
where \(\tau \in \R^k\) is a vector of generalized input forces and the input
matrix \(B \in \R^{n \times k}\) is assumed to be full rank \(k < n\).

It is easy to show that \eqref{eqn:hamiltonian-eom-general} reduces to
\begin{equation}\label{eqn:hamiltonian-full-dynamics}
     \begin{cases}
        \dot{q} = D\inv(q)p \\
        \dot{p} = -\frac{1}{2} (\Id{n} \otimes p\tpose) \nabla_q D\inv(q) p
        - \nabla_q P(q) + B(q) \tau
        . \\
    \end{cases}
\end{equation}

@@

%---------- Bibliography ----------%
\bibliography{bib}
\end{document}
%/========== /Main Document ==========/%
% vim: set tw=80 ts=4 sw=4 sts=0 et ffs=unix :
